Linking Gamification, Ludology and Pedagogy: How to Use Serious Games for Various Knowledge Domains\\

### 2021-11-01 Article/main.tex
Updates
Updated Article -> Synthesis

\subsection{Initial Knowledge Domain Recommendations}
Kapp\cite{Kapp2012a}, in addition to providing definitions of the various knowledge domains, provides some ways that each domain can be taught to best relay that particular type of knowledge. While these reconsiderations are derived under a gamification perspective, that can just as easily be applied for a digital game.

\begin{itemize}
\item
Games that would involve some form of sorting and matching are ideal for teaching declarative knowledge\cite{Kapp2012a}.
\item
Conceptual knowledge is beast taught through demonstrations and once again a sorting type game where the sorting is based on the common trait of the content or topic\cite{Kapp2012a}.
\item
A demonstration that displays the failure of not complying with the rules is helpful for a topic under the rules-based knowledge domain\cite{Kapp2012a}.
\item
Procedural knowledge is best taught through having the learners work through the procedure itself in some means\cite{Kapp2012a}.
\item
Soft Skills are best taught through having the learner repeatedly apply the skill in question u=in various scenarios\cite{Kapp2012a}.
\item
Immersing the learner within a phenomena found in the affective knowledge domain is a neffective means of teaching them about it\cite{Kapp2012a}.
\item
Kapp\cite{Kapp2012a} states that observation is an ideal method of teaching the learner about a topic in this domain.
\end{itemize}

@@

@@

Learning through play, such as a serious game, is an effective way to implement all of these methods\cite{allers2021children} and as such provides an additional framework targeted specifically at younger children as opposed to the previous studies\cite{Dincelli2020,Sheng2007} which were focused on adults. While this list does not provide direct principles to follow during the design process, including ways for these methods of learning to be present in a serious game should also be taken into consideration.
\\\\
In addition to the above, the study also made use of several elements identified by Callaghan \textit{et al.}\cite{callaghan2018} which are based off how young children, namely preschoolers, learn. The first of these is \textit{clear and simple goals} which is concerned with presenting a user with concise outcomes to work towards\cite{callaghan2018}. Similarly with Anti-phishing phil\cite{Sheng2007}, is the element of \textit{quality of feedback and rewards} which deals with how feedback is presented to a user - for example preschoolers may not yet be able to read and as such the feedback must be structured accordingly such as making use of simple visuals\cite{allers2021children}. The next element is \textit{Structure of the challenge} consists of setting the difficulty of tasks and changing the difficulty depending on how the user is performing\cite{callaghan2018}. This element can also be described using some of the corollaries from Merril's First Principles\cite{Merrill2002} - which will be discussed in the following section. The last element Callaghan \textit{et al.}\cite{callaghan2018} is that of \textit{Motion based learning} which describes the physical interaction a user will have with applications which in this case would be designing larger touch controls to account for a preschool child's current level of motor functions. This particular aspect is almost certainly vital when dealing with any knowledge from the psycho motor domain.
\\\\
As previously mentioned, this case study has not yet developed the serious game and as such cannot be tested by users. However, a expert review was conducted on the design of this serious game of which the outcomes were largely positive as the reviewers "found the implementations of each element satisfactory"\cite{allers2021children}.

@@

\section{Synthesis from Research}
\subsection{Recommendations per Knowledge Domain}

@@

\section{Conclusion}
This study discussed the current state of the paradigms that instructional institutions are based off of and how society has progressed and developed different needs than the systems in place currently provide. As such, research into how serious games can be used in an educational environment was conducted with specific focus on the fields of pedagogy, ludology and gamification in order to answer the question, \textit{what qualities are required for a serious game to be effectively used in an educational environment on various topics}. Through a literature review in these fields, various instructional theories were found that could be helpful to answer the question as they are able to be translated into the context of games relatively easy. Furthermore, several research papers were used as case studies to discover what design principles are typically followed in the development of serious games. This information was then used to....

>>>>

\subsection{Initial Knowledge Domain Recommendations}
Kapp\cite{Kapp2012a}, in addition to providing definitions of the various knowledge domains, provides some ways that each domain can be taught to best relay that particular type of knowledge. While these recommendations are derived under a gamification perspective\cite{Kapp2012a}, that can just as easily be applied for a digital game:

\begin{itemize}
\item
Games that would involve some form of sorting and matching are ideal for teaching declarative knowledge.
\item
Conceptual knowledge is beast taught through demonstrations and once again a sorting type game where the sorting is based on the common trait of the content or topic.
\item
A demonstration that displays the failure of not complying with the rules is helpful for a topic under the rules-based knowledge domain.
\item
Procedural knowledge is best taught through having the learners work through the procedure itself in some means.
\item
Soft Skills are best taught through having the learner repeatedly apply the skill in question u=in various scenarios.
\item
Immersing the learner within a phenomena found in the affective knowledge domain is an effective means of teaching them about it.
\item
Kapp\cite{Kapp2012a} states that observation is an ideal method of teaching the learner about a topic in the psychomotor domain.
\end{itemize}

@@

\\\\\\

@@

Learning through play, such as a serious game, is an effective way to implement all of these methods\cite{allers2021children} and as such provides an additional framework targeted specifically at younger children as opposed to the previous studies\cite{Dincelli2020,Sheng2007} which were focused on adults. While this list does not provide direct principles to follow during the design process, including ways for these methods of learning to be present in a serious game should also be taken into consideration.
\\\\
In addition to the above, the study also made use of several elements identified by Callaghan \textit{et al.}\cite{callaghan2018} which are based off how young children, namely preschoolers, learn. The first of these is \textit{clear and simple goals} which is concerned with presenting a user with concise outcomes to work towards\cite{callaghan2018}. Similarly with Anti-phishing phil\cite{Sheng2007}, is the element of \textit{quality of feedback and rewards} which deals with how feedback is presented to a user - for example preschoolers may not yet be able to read and as such the feedback must be structured accordingly such as making use of simple visuals\cite{allers2021children}. The next element is \textit{Structure of the challenge} consists of setting the difficulty of tasks and changing the difficulty depending on how the user is performing\cite{callaghan2018}. This element can also be described using some of the corollaries from Merril's First Principles\cite{Merrill2002} - which will be discussed in the following section. The last element Callaghan \textit{et al.}\cite{callaghan2018} is that of \textit{Motion based learning} which describes the physical interaction a user will have with applications which in this case would be designing larger touch controls to account for a preschool child's current level of motor functions. This particular aspect is almost certainly vital when dealing with any knowledge from the psychomotor domain.
\\\\
As previously mentioned, this case study has not yet developed the serious game and as such cannot be tested by users. However, a expert review was conducted on the design of this serious game of which the outcomes were largely positive as the reviewers "found the implementations of each element satisfactory"\cite{allers2021children}.

@@

\section{Synthesis from Research}
From the literature and case studies examined, there are several key qualities that they share among each other either under the same descriptor or with similar descriptions with different names. It is these qualities that will form the basis to answer the question posed in the beginning of this study.
\\\\
The first quality is shared amongst Merrill's First Principles\cite{Merrill2002} and two of the case studies\cite{Dincelli2020,Sheng2007}. \textit{Reflection} is then a vital quality to a serious game if intended to be used in an educational environment and is described as giving a user some time after being presented with new knowledge or a task to dwell on what they have experienced.
\\\\
The second quality a serious game should make use of is that of \textit{Feedback}. All of the case studies\cite{Dincelli2020,Sheng2007,allers2021children} mention as such and Merrill\cite{Merrill2002} refers to it under the diminishing coaching corollary. A user should be presented with feedback on how they are progressing on a given set of tasks within the game at some point and as they progress the amount of feedback should be slowly diminished. The feedback amount should also be tied to the performance of the user - increasing if they begin to struggle and decrease if not. Since feedback can take on many different forms, the type of feedback as well as the method of delivery is dependant on the topic being taught.
\\\\
Another quality that should be implemented is that the serious game should showcase and teach topics through the use of \textit{Story-telling}. The case studies\cite{Dincelli2020,Sheng2007,allers2021children} all mention the use of this and John Keller's ARCS model\cite{keller1987development}, specifically under the attention element, also states that this is a proponent of keeping users engaged. A game should then allow for a story to take place during the teaching of a topic which can also be done in several ways - such as contextually with Anti-phishing phil or as the main focus of the topic as with the SETA artefact\cite{Dincelli2020} and Happy Hippo\cite{allers2021children}. Another means to accomplish this is to make use of an agent that guides the user through the game. 
\\\\

\subsection{Recommendations per Knowledge Domain}

@@

\section{Conclusion}
This study discussed the current state of the paradigms that instructional institutions are based off of and how society has progressed and developed different needs than the systems in place currently provide. As such, research into how serious games can be used in an educational environment was conducted with specific focus on the fields of pedagogy, ludology and gamification in order to answer the question, \textit{what qualities are required for a serious game to be effectively used in an educational environment on various topics}. Through a literature review in these fields, various instructional theories were found that could be helpful to answer the question as they are able to be translated into the context of games relatively easy. Furthermore, several research papers were used as case studies to discover what design principles are typically followed in the development of serious games. This information was then used to identify what are the major qualities which a serious game should have in order to be effective in a educational environment as well as providing specific recommendations for various knowledge domains. The qualities identified were allowing for Reflection, providing Feedback, making use of Story elements and Structuring.
